The Astropy Project

### 2017-11-22 main.tex
update commits section with new figure

As of version 2.0, \astropypkg contains $212244$ lines of code\footnote{This
line count includes comments, as these are often as important for
maintainability as the code itself.  Without comments there are $142197$ lines
of code.} contributed by $232$ unique contributors over $19270$ \texttt{git}
commits. We can construct a distribution of the number of commits
per contributor ordered by decreasing number of commits. When doing this,
we find that this distribution
follows an approximate power-law (with log-slope of
$\approx -0.5$), meaning most of the commits were and are contributed by a
relatively small fraction of the contributor pool.
Roughly half of the commits were contributed by the top $4$
contributors, while $\sim 90$ percent of the commits came from the top $24$
contributors.

>>>>

\begin{figure}
\includegraphics[width=\textwidth]{ncommits.pdf}
\caption{%
    \emph{Left panel}: Distribution of number of commits per committer.
    \emph{Right panel}: Cumulative number of commits to the \astropypkg core
    package over time.
    \label{fig:ncommits}
}
\end{figure}

As of version 2.0, \astropypkg contains $212244$ lines of code\footnote{This
line count includes comments, as these are often as important for
maintainability as the code itself.  Without comments there are $142197$ lines
of code.} contributed by $232$ unique contributors over $19270$ \texttt{git}
commits.
\figurename~\ref{fig:ncommits}, left, shows the distribution of total number of
commits per contributor as of November 2017; from this, it's clear that most
commits were and are contributed by a relatively small fraction of the
contributor pool.
\figurename~\ref{fig:ncommits}, right, shows the number of contributors as a
function of time since the genesis of the \astropypkg core package.
